---
title: "Data Modeling Using Caret"
output: html_document
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
knitr::opts_chunk$set(fig.path = "figure/")
```

## Loading Concrete Data from AppliedPredictiveModeling
I am modeling the concrete data from library "Applied Predictive Modeling". Here's a summary of the data:
```{r load}
library(AppliedPredictiveModeling)
data(concrete)
summary(concrete)
```

I will then partition the data into the train, test buckets

```{r partition}
library(lattice)
library(ggplot2)
library(caret)
library(Hmisc)
library(dplyr)
set.seed(1000)
inTrain = createDataPartition(mixtures$CompressiveStrength, p = 3/4)[[1]]
training = mixtures[ inTrain,]
testing = mixtures[-inTrain,]
```

## Plots
Some plot to understand the data

```{r superplasticizer}
hist(concrete$Superplasticizer)
```

Shows that the "Superplasticizer" variable is quite skewed

```{r CompressiveStrength}
FlyAsh_lev <- cut2(concrete$FlyAsh)

Age_lev <- cut2(concrete$Age)
plot(concrete$CompressiveStrength, type='p', col=FlyAsh_lev)
##legend(2.8,-1,cement_lev, pch = c(1,2), lty = c(1,2))
cor(concrete$CompressiveStrength,concrete$Age)
```

## Alzheimer's data
```{r Alzheimers data}
set.seed(3433)
data(AlzheimerDisease)
adData = data.frame(diagnosis,predictors)
inTrain = createDataPartition(adData$diagnosis, p = 3/4)[[1]]
training = adData[ inTrain,]
testing = adData[-inTrain,]
colnames(predictors)
```
By default, caret keeps the components that explain 95% of the variance. But you can change it by using the tresh parameter. You can also set a particular number of components by setting the pcaComp parameter.

```{r preprocess}
newdata<-select(training, starts_with("IL"))

#preProc<-preProcess(newdata,method="pca",preProcOptions = list(thresh = 0.8))
res.pca <- prcomp(newdata, scale = TRUE)
summary(res.pca)
```

showing that you need 8-9 PCA components to capture 90% of the variance.

```{r PCA confusionMat}
diags <-training$diagnosis
newdata <- data.frame(diags, newdata)
preProc <- preProcess(newdata[,-1],method="pca", thresh=0.8)
trainPC <- predict(preProc, newdata[,-1], method="glm")
trainPC<-data.frame(diags,trainPC)
modelFit <- train(diags ~ ., method="glm", data=trainPC)

testPC <- predict(preProc, testing[,-1])
confusionMatrix(testing$diagnosis, predict(modelFit, testPC))
```
PCA accuracy is 0.7195 $\sim$ 0.72.

The non-PCA accuracy
```{r nonPCA}
nonPCAModelFit <- train(diags~., data=newdata,method="glm")
newtesting <- data.frame(testing$diagnosis, select(testing, starts_with("IL")))

testpredict <- predict(nonPCAModelFit,newtesting[,-1])

confusionMatrix(testpredict,testing$diagnosis)
```

Showing an accuracy of 65%.
